---
title: "Drought detection in the Omineca"
author: "Hardy Griesbauer"
date: "20/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(tidyverse)
library(bcdata)
library(mapview)
library(here)

# Load data
load(here("data","droughtData.RData"))

```

# Drought damage in the Omineca Region
I tried to use the `bcdata` package to query and download forest health polygon data, but at the time it wasn't updated with 2019 data.  I downloaded 2019 and 2018 AOS polygons from https://www.for.gov.bc.ca/ftp/HFP/external/!publish/Aerial_Overview/, and filtered for the following factors:

1. NDM = drought mortality;
2. ND = drought damage;
3. NE = flagging in cedar (phenomenon observed in Robson Valley); and
4. NF = foliar damage from drought.

We can then filter for Omineca region and explore on a map:

```{r explore drought ROM}

droughtData %>%
  filter(REGION %in% c("ROM")) %>% # filter for Omineca (ROM)
  filter(!SEVERITY %in% c("L")) %>% # filter out low severity 
  
    # Map
  mapview(zcol="FHF")


droughtData %>%
  filter(REGION %in% c("ROM")) %>% # filter for Omineca (ROM)
  filter(!SEVERITY %in% c("L")) %>% # filter out low severity 
  sf::write_sf("data/drought_poly_aos.shp")
```


